The Effect of Events on Australian Parliamentary Discussion (1851--2017)

### 2018-10-13 outputs/docs/events/paper.Rmd
more paper changes

The STM is set-up to most easily include metadata to do with prevalence and content. Prevalence relates to the topic proportions in each document. For instance, we expect that topics related to the reasons for Federation, such as tariffs and trade, should be more prevalent in those earlier years than later. Similarly, we may expect topics to do with terrorism to be more prevalent in recent years. Content relates to the words that make up each topic. For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic. The prevalence meta-data for the $d$th document are in $X_d$, which has one column for each aspect. For instance, if there were 10 documents and each had a date and an author, then $X$ would be $10\times 2$. Similarly, the content meta-data are

@@

The STM framework allows for covariates to be included in the estimation of the topic distributions, $\theta_d$ (see equation **[XX]** above). This allows the certain types of relationships between topics and events to be assessed. However, there are several limitations to the STM covariate framework in this context:

@@

To overcome these challenges, we formalize a statistical framework which allows us to systematically identify significant changes in topic distributions over time. Specifically, we use a Bayesian hierarchical Dirichlet regression framework which relates proportions of each topic to underlying time trends, changes in goverments and elections.

Define $\gamma_{dp}$ to be the proportion of topic of topic $p$ on day $d$. Note that $\gamma_{d,1:P}$ for $p = 1,2,\dots P=40$ is equal to the estimated values of $\theta_d$ from the STM. We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart. Using this definition, there are a total of 745 sitting periods across all years of interest (1901--2017).

>>>>

The STM is set-up to include metadata to do with prevalence and content. Prevalence relates to the topic proportions in each document. For instance, we expect that topics related to the reasons for Federation, such as tariffs and trade, should be more prevalent in those earlier years than later. Similarly, we may expect topics to do with terrorism to be more prevalent in recent years. The prevalence meta-data for the $d$th document are in $X_d$, which has one column for each covariate. For instance, if there were 10 documents and each had a date and an author, then $X$ would be $10\times 2$. Content relates to the words that make up each topic. For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic. STM only allows for one covariate related to content changes, for example, documents could be grouped by year.

@@

As mentioned above, the STM framework allows for covariates to be included in the estimation of prevalence of topcs, $\theta_d$ (see equation **[XX]** above). This theoretically would allow certain types of relationships between topics and events to be assessed. However, there are several limitations to the STM covariate framework in this context:

@@

To overcome these challenges, we formalize a statistical framework which allows us to systematically identify significant changes in topic distributions over time. Specifically, we use the estimated topic distributions from STM as an input into a Bayesian hierarchical Dirichlet regression framework, which relates proportions of each topic to underlying time trends, changes in goverments and elections. This set-up also allows us to identify 'outlying' topic distributions and relate these to other, non-scheduled political events.

Define $\gamma_{dp}$ to be the proportion of topic of topic $p$ on day $d$. Note that the $\gamma_{d,1:P}$ for $p = 1,2,\dots P=40$ are equal to the estimated values of $\theta_d$ from the STM. We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart. Using this definition, there are a total of 745 sitting periods across all years of interest (1901--2017).
